\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-25 manuscript/manuscript.tex
fixed parentheses error

The neural network with 1 hidden layer performed poorly with 72.5\% accuracy. However, the 1 hidden layer model had the highest precision 97.8\% of the models (93.1\% for 5 hidden layers, 94.7\% for 10 hidden layers, 88.0\% for 15 hidden layers). The poor accuracy for the 1 hidden layer model was accounted for with a low negative predictive value (54.7\%); 86.1\% for 5 hidden layers, 97.0\% for 10 hidden layers, 100\% for 15 hidden layers). It was determined that the most accurate model was the neural network with 10 hidden layers (95.4\% accuracy; 72.5\% for 1 hidden layer, 90.8\% for 5 hidden layers, 90.8\% for 15 hidden layers).

An ROC curve was plotted for each of the neural network variants as an alternative evaluative method (Fig. \ref{fig:nnet}). The relative ratio between the model’s false positive rate (FPR) and its true positive rate (TPR) were averaged between 5 k-folds. The mean AUC for the 5 trials was used to compare the four network architectures. However, the differences between the various architectures for AUC was not significantly different. Consequently, confusion matrices (Fig. \ref{fig:nnet}) and associated misclassification rates were used to pick the optimal model. The neural net with 10 hidden layers demonstrated the best performance overall with a 95.4\% accuracy.

>>>>

The neural network with 1 hidden layer performed poorly with 72.5\% accuracy. However, the 1 hidden layer model had the highest precision 97.8\% of the models (93.1\% for 5 hidden layers, 94.7\% for 10 hidden layers, 88.0\% for 15 hidden layers). The poor accuracy for the 1 hidden layer model was accounted for with a low negative predictive value (54.7\%; 86.1\% for 5 hidden layers, 97.0\% for 10 hidden layers, 100\% for 15 hidden layers). It was determined that the most accurate model was the neural network with 10 hidden layers (95.4\% accuracy; 72.5\% for 1 hidden layer, 90.8\% for 5 hidden layers, 90.8\% for 15 hidden layers).

An ROC curve was plotted for each of the neural network variants as an alternative evaluative method (Fig. \ref{fig:nnet}). The relative ratio between the model’s false positive rate and its true positive rate were averaged between 5 k-folds. The mean AUC for the 5 trials was used to compare the four network architectures. However, the differences between the various architectures for AUC was not significantly different. Consequently, confusion matrices (Fig. \ref{fig:nnet}) and associated misclassification rates were used to pick the optimal model. The neural net with 10 hidden layers demonstrated the best performance overall with a 95.4\% accuracy.
